First Draft

### 2021-05-13 draft.Rmd
more background

@@

>>>>

The dataset contains data from 5110 patients. It is pretty evenly split with gender, 59% female and 41% male. The binary variables hypertension and heart disease are much less balanced, with only 9.75% of the patients having hypertension and 5.40% of them having heart disease. According to the American Heart Association, almost half of adults in the U.S. have hypertension, or chronically high blood pressure, which is directly related to heart disease. So, the dataset may not accurately represent the population, but it could still be used to analyze predictive factors for strokes. The prevalence of stroke in this dataset is 4.87%.

@@

https://www.cdc.gov/bloodpressure/facts.htm#:~:text=Nearly%20half%20of%20adults%20in,are%20taking%20medication%20for%20hypertension.&text=Only%20about%201%20in%204,have%20their%20condition%20under%20control.

https://www.sciencedaily.com/releases/2019/01/190131084238.htm#:~:text=01%2F190131084238.htm-,At%20least%2048%20percent%20of%20all%20adults%20in%20the%20United,according%20to%20the%20latest%20statistics.
